---
title: "Simulation of data"
author: "YK"
date: "2020/10/8"
output: pdf_document
---

```{r setup, include=FALSE}
# Code for setting up
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
```

# Data Simulation

We should have total 6 variables obtained from the results of survey.

## Age

(1) For age, from Statistics Canada we've known the number of people of each age group in Ontario population, in this case we divide population into 4 groups(0--18, 19--49, 50--89, 90 and over), and by calculation the percentages are 21%, 41.1%, 37% and 0.9% respectively.

```{r}
# Size of population(Number of simulations)
N<-100000
set.seed(538)
# Age
# We assume in each age group, ages appears at equal probability, so it follows a uniform distribution.
Age_0_18<-runif(N* 0.21, min = 0, max = 18)
Age_19_49<-runif(N*0.41, min = 19, max = 49)
Age_50_89<-runif(N*0.37, min = 50, max = 89)
Age_90_over<-runif(N*0.010, min = 90, max = 110)
#This is the simulated Age data
Age_all<-c(Age_0_18, Age_19_49, Age_50_89, Age_90_over)
# Shuffle the data
ShAge_all<-sample(Age_all)

```

## Gender

(2)For Gender, we assume the ratio of female and male is 1:1.

```{r}
set.seed(233)
#Gender
gender<-c("Female","Male")
Gender_all<-sample(gender, N, replace = T)
```

## District

(3) For district the person is living in, there are total 124 districts in Ontario, we assume each person has the equal probability to live in any district.

```{r}
set.seed(304)
#District
District<-sample(1:124, N, replace = T)
```

## Supporting Political party

(4) We referenced the results of election in 2019 and will simulate according to the vote share in Ontario.

*LIB: 41.4%

*CON: 33.2%

*NDP: 16.8%

*GRN: 6.2%

*IND: 0.4%

*PP: 1.6%

*OTH: 0.4%

```{r}
set.seed(347)
#Political Party supported
#Simulate according to the past vote share
Poli_Parties<-c("LIB","CON","NDP","GRN","IND","PP","OTH")
PoliticalP_supported<-sample(Poli_Parties,N,prob = c(0.414, 0.332, 0.168, 0.062, 0.004, 0.016, 0.004), replace = T)
```

## Education Level

(5)We referenced from the 2016 education attainment status in Canada, and will simulate according to this.

*Bachelor's degree or higher: 28.5%

*University below bachelor's	3.1%

*College diploma	22.4%

*Apprenticeship or other trades certificate	10.8%

*High school diploma	23.7%

*No certificate, diploma or degree	11.5%

```{r}
set.seed(302)
#Education level
Edu_levels<-c("Bachelor or higher","University below bachelor's", "College diploma","Apprenticeship or other","High school","No certificate, diploma or degree")
Edu_level_all<-sample(Edu_levels, N, prob = c(0.285, 0.031, 0.224, 0.108, 0.237, 0.115),replace = T)
```

## Income

(6)We simulate income in the same way we simulate age.

```{r}
set.seed(303)
#Income
Income_1<-runif(N*0.2, min = 0, max = 19000)
Income_2<-runif(N*0.2, min = 19001, max=24000)
Income_3<-runif(N*0.2, min = 24001, max = 37000)
Income_4<-runif(N*0.2, min = 37001, max = 56000)
Income_5<-runif(N*0.2, min = 56001, max = 65000)

#2018
Income_under_20000<- runif(N*0.268, min = 0, max = 19999)
Income_20000_75000<- runif(N*0.547, min = 20000, max = 74999)
Income_75000_over<- runif(N*0.185, min = 75000, max = 250001)
Income_all<-c(Income_under_20000, Income_20000_75000, Income_75000_over)
#shuffle
Income<-sample(Income_all)
```

Now we combine together

```{r}
set.seed(305)
All_together.df<-data_frame(ShAge_all, Gender_all, PoliticalP_supported, Edu_level_all, Income, District)
sample_selcet_rows<-sample(N,20000)
sample_dataset<-All_together.df[sample_selcet_rows,]
```


